\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{RAKESH KUMAR} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91 8825189599 \\ Bangalore, karnataka} 
\address{\href{mailto:rakeshcse123@gmail.com}{rakeshcse123@gmail.com} \\ \href{https://www.linkedin.com/in/rakesh-kumar18/}{linkedin.com/in/rakesh-kumar18/} \\ \href{https://github.com/aarvi18}{github.com/aarvi18}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Results-oriented coder passionate about problem-solving and innovation, seeking a challenging role to apply technical expertise and collaborate with a dynamic team. Committed to contributing to the development of cutting-edge solutions in a growth-oriented organization.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Engineering in Computer Science} \hfill {2020 - Present}\\
Acharya Institute of Technology, Bangalore Karnataka.

{\bf Senior Secondary} \hfill {2018 - 2019}\\
Shivam International School, Patna, Bihar.

{\bf Secondary School} \hfill {2016 - 2017}\\
Patna Convent, Patna, Bihar.
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & JavaScript, React.Js, Node.Js, MongoDB, Express.Js, HTML, CSS, MySQL, RESTful API
\\
Familiar with & Redux, TypeScript, Next.JS, Unit Testing, Git and GitHub \\
\end{tabular}\\
\end{rSection}

\begin{rSection}{INTERNSHIP EXPERIENCE}

\textbf{Full Stack Web Developer} \hfill Oct 2023 - Jan 2024\\
Curiosense Innovation Pvt Ltd \hfill \textit{Bangalore, Karnataka}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Developed and maintained MERN stack applications, ensuring seamless functionality and optimal user experience.
     \item Implemented scalable and efficient solutions for full-stack web development, contributing to the success of diverse
projects in a dynamic team environment.
 \end{itemize}
 
\textbf{Backend Developer} \hfill Aug 2023 - Oct 2023\\
DezainaHub \hfill \textit{Bangalore, Karnataka}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Spearheaded backend development at DezainaHub, crafting robust solutions and ensuring optimal performance for the
platform's architecture.

     \item Engineered scalable and efficient backend systems, playing a pivotal role in enhancing functionality and contributing to
the success of projects at DezainaHub.

 \end{itemize}

 \textbf{Full Stack Web Developer} \hfill June 2023 - Aug 2023\\
iNeuron.ai \hfill \textit{Bangalore, Karnataka}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Drove full-stack development at iNeuron.ai, innovating and optimizing an online MERN-based Cake order system for
seamless user interactions.

     \item Contributed to the success of iNeuron.ai by architecting and maintaining a comprehensive MERN stack solution,
enhancing the efficiency and functionality of the online cake ordering platform.

 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Text-to-Image.} \href{https://hiring-search.careerflow.ai/}{(Try it here)}
{\begin{itemize}
    \itemsep -3pt {} 
     \item Developed front-end UI in React.js, ensuring responsiveness and cross-browser compatibility.
     \item Integrated third-party libraries for text processing and image rendering, optimizing performance.
 \end{itemize}
 }
\item \textbf{Blog Web App.} \href{https://hiring-search.careerflow.ai/}{(Try it here)}
{\begin{itemize}
    \itemsep -3pt {} 
     \item Developed a robust blog web app with React.js and Redux frontend, ensuring high performance and user experience.
     \item Integrated Appwrite backend for enhanced security and seamless data management, resulting in a production-ready application.
 \end{itemize}
 }
 \item \textbf{Online Cake Order e-commerce.} \href{https://hiring-search.careerflow.ai/}{(Try it here)}
{\begin{itemize}
    \itemsep -3pt {} 
     \item Orchestrated the full-stack development of an online cake ordering system with MERN technology.
     \item Engineered a scalable backend infrastructure, ensuring secure data management and system efficiency.
     \item Designed a responsive and intuitive front-end interface using React.js for an enhanced user experience.
 \end{itemize}
 }
 \item \textbf{Real Time Chat Application.} \href{https://hiring-search.careerflow.ai/}{(Try it here)}
{\begin{itemize}
    \itemsep -3pt {} 
     \item Developed and deployed a Real-Time Chat Application with Socket.io and Node.js.
     \item Showcased proficiency in JavaScript, emphasizing real-time communication and server-side development.
     \item Implemented robust security measures for data confidentiality and integrity.
 \end{itemize}
 }
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements} 
\begin{itemize}
    \item  Problem solving profile \href{https://www.faangpath.com/blog/}{LeetCode} and  \href{https://www.faangpath.com/blog/}{Coding Ninja}.
\item   Conducted a Hackathon- SAQATHON in our college Acharya Institutes of Technology.
\item  Participated in a Hackathon organized by iNeuron.ai and partnered with GeekyAnts.
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Leadership} 
\begin{itemize}
    \item Coding Club President of Developer’s Club of Acharya in college.
    \item Led the seamless organization of Bangalore Biggest college cultural fest Acharya Habba’23, overseeing end-to-end event
management responsibilities with a focus on strategic planning, meticulous execution, and effective stakeholder.
\end{itemize}


\end{rSection}


\end{document}
